% status: 30
% chapter: TBD

\title{Twitter Sentimental Analysis with Spark}


\author{Venkatesh Aditya Kaveripakam}
\affiliation{%
\institution{Indiana University}
\city{Bloomington}
\state{IN}
\postcode{47408}
\country{USA}}
\email{vekave@iu.edu}

\author{Surya Prakash Sekar}
\affiliation{%
\institution{Indiana University}
\city{Bloomington}
\state{IN}
\postcode{47408}
\country{USA}}
\email{sursekar@iu.edu}

% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{Aditya}{Surya}


\begin{abstract}

\end{abstract}

\keywords{hid-sp18-411,hid-sp18-408, Swagger, Spark, API, Cloud, Twitter}


\maketitle

\section{Introduction}
In this project we aim to build a RESTful webservice that will accept a topic
of interest as input from the user and query the relevant hashtag data from
the twitter API using python cursors. All pre-processing involved with the
tweets data will be handled with the help of in-built python libraries and a
consumable dataset for spark would be created. SparkML library is then used
to perform sentimental analysis on the tweets data and a summary is provided
with respect to it. One of the potential problem to our service would be its
ability to fetch enough tweets perform sentiment analysis and produce a
reliable result.

Apache Spark is an open source cluster computing framework that is the
successor to Apache Hadoop. The micro-batch processing capabilities and high
speed of spark make it. Apache Spark also bundles libraries for applying
machine learning and graph analysis techniques to data at scale.
The web service will be deployed on Chameleon Cloud and tested for uniform
performance and scalability. Chameleon cloud is a cloud learning
platform/testbed provided by Computation Institute (CI) at the University of
Chicago and Argonne National Laboratory and the Texas Advanced Computing
Center (TACC)~\cite{hid-sp18-418-chameleon-about}.


\bibliographystyle{ACM-Reference-Format}
\bibliography{report} 